\mychapter{The GBTSTATUS IF Path Nomenclature}\label{appendix:gbtstatus}

The nomenclature used for the \gls{IFpath} information in the \gls{Astrid} Status Tabs:
\begin{description}[leftmargin=*]
\item[{\bf IF}\#] The \# displayed is the number corresponding to the \gls{IFRack} 
switch in use. The value displayed is the \gls{RF} power in Volts detected by the 
\gls{IFRack}. 
\item[{\bf CM}\#] The \# displayed is the number corresponding to the Converter 
Module in use. The value displayed is the \gls{RF} power in Volts coming out of the 
Converter Module after the \gls{LOtwo} and \gls{LOthree} mixers and before the Converter
Module filters. 
\item[{\bf CF}\#] The \# displayed is the number corresponding to the Analog 
Filter in use. The value displayed is the \gls{RF} power in Volts coming out of the 
\gls{AFRack} after all filters have been applied (used with 100MHz Converters).
\item[{\bf SG}\#] The \# displayed is the number corresponding to the Analog 
Filter in use. The value displayed is the \gls{RF} power in Volts coming out of the 
\gls{AFRack} after all filters have been applied (used with 1.6~GHz Samplers.
\item[{\bf VEGAS-J}\#] The \# displayed is the number corresponding to the port 
of \gls{VEGAS} in use. The value displayed is the power level in dBFS. For best
performance, it should be approximately -20 dBFS.
\item[{\bf Radar-Port}\#] The \# displayed is the number corresponding to the port
of the Radar in use.
\item[{\bf DCR-Port}\#] The \# displayed is the bank and number corresponding to 
the port of the \gls{DCR} in use. The value displayed is the total power in raw
counts. 
\item[{\bf TSys}\#] The \# displayed is the number corresponding \gls{DCR} port
in use. The value displayed is the system temperature as reported by the \gls{DCR}
(should be considered a loose approximation).
\item[{\bf backendIF}] The value displayed is the frequency of the Doppler track 
rest frequency as seen by the backend, in GHz.
\end{description}

%\item[{\bf ACS-Port \#}] The \# displayed is the number corresponding to the port 
%of the Spectrometer in use. The value displayed is the duty cycle in 
%db \footnote{$x$ represented in db is given by $10 \log{x}$}.
%This value is relative to the optimum power level; for best performance, it should
%be between -3 and +3 db.
%\item[{\bf SPP-Port \#}] The \# displayed is the number corresponding to the port 
%of the \gls{SP} in use. The value displayed is the power level in db.