\chapter{After Your Observations}\label{chap:after}

%++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\section{Taking your data home}

All data must be transferred over the internet to your home institution.
Several methods are available for this such as the scp utility shown below.
If you wish to transfer more than a few hundred GigaBytes, please contact
the computing department at helpdesk-gb@nrao.edu for assistance.  For more
general questions or advice, please contact your \gls{GBT} \dq{friend}.

{\tt
[you@yourmachine $\sim$]\$ scp you@GBTmachine:data.fits datacopy.fits
}

%++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\section{Installing GBTIDL}

Most spectral line observers will use \gls{GBTIDL} to reduce their data.
If you have an IDL licence at your home institution then you can obtain
a copy of \gls{GBTIDL}, the user guide and installation instructions from
\htmladdnormallink{http://gbtidl.nrao.edu}{http://gbtidl.nrao.edu}.
Otherwise, feel free to continue using your \gls{GBT} Linux account for
data reduction.

%++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\section{Keep Your Contact Person Informed}

Don't hesitate to ask your scientific contact person if you are having
trouble reducing your data, or if you have questions about your data.
It does not matter how long its has been since you observed, your contact
person will be happy to help you.

%++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\section{Press Releases and News-worthy Items}

News-worthy items should be discussed with the \gls{NRAO} press officer.
The press officer can help write an \gls{NRAO} press release or a press
release from your home institution.  For more information see
page 30 of the January 2007 version of the \gls{NRAO} Newsletter
\hfil\break
(\htmladdnormallink{http://www.nrao.edu/news/newsletters/nraonews110.pdf}{http://www.nrao.edu/news/newsletters/nraonews110.pdf}).

%++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\section{Publishing Your Results}

Finally you should publish your results.  The \gls{NRAO} will help with page
charges for the publication of the results from your observations.  Please
see \htmladdnormallink{http://www.nrao.edu/library/page\_charges.shtml}{http://www.nrao.edu/library/page_charges.shtml} for more details.
{\bf Please inform your scientific contact person of any publication resulting
from your observations.}
