\chapter{Computing}\label{chap:computing}

\subsection{Accounts}
New observers should obtain a Green Bank Linux computing account as soon as possible.
Before receiving your account you will have to go through a screening process.
This screening will automatically happen for visiting observers making a
room reservation in the BOS system.  You can also begin the screening
process by filling in the form at
\htmladdnormallink{https://info.nrao.edu/oas/dpscompliance}
{https://info.nrao.edu/oas/dpscompliance}.

Accounts may be requested from helpdesk-gb@nrao.edu.
Any problems with connecting a personal computer to our network should also
be referred to the helpdesk.
Please note that accounts will be archived after approximately two years of
inactivity but can be reactivated upon request.

\subsection{Computing Facilities}
Workstations with access to both Windows and Linux servers are available
for visitors at the Observer Periphery (Room 105) in the Jansky Lab.
Laptop connections are provided there and in several locations around the
Observatory, including some rooms in the residence hall.  Additional
workstations can be found in the residence hall lounge and Jansky Lab library.

\subsection{Remote Access and VNC}

You will need to access the Green Bank Linux system remotely
for script preparation, remote observations, and data reduction.

Scheduling blocks (scripts that perform astronomical observations)
should be prepared and uploaded into \gls{Astrid} (see Chapter~\ref{chap:astrid})
well in advance of any observations or first
time visits.  In order to run Astrid all observers must ensure they can connect
to our network via \gls{VNC} .  Detailed instructions
for setting up \gls{VNC} on Linux, Mac OS X, and Windows can be found at
\htmladdnormallink{https://science.nrao.edu/facilities/gbt/observing/remote-observing-with-the-gbt}{https://science.nrao.edu/facilities/gbt/observing/remote-observing-with-the-gbt}.

When starting a new \gls{VNC} session please remember that the \textit{stargate} host,
along with the machines \textit{titania} and \textit{ariel} are reserved
exclusively for remote observations. For all other purposes please use
\textit{prospero} (ssh.gb.nrao.edu) as the host, and one of the data reduction
machines listed in \\
\htmladdnormallink{http://www.gb.nrao.edu/pubcomputing/data-reduction.shtml}
{http://www.gb.nrao.edu/pubcomputing/data-reduction.shtml}.

Observers wishing to reduce VEGAS data will need access to the \dq{lustre} file system.
Refer to
\htmladdnormallink{http://www.gb.nrao.edu/pubcomputing/public.shtml}
{http://www.gb.nrao.edu/pubcomputing/public.shtml} for a list of lustre clients.

