\chapter{How To Use This Manual}

This document provides the necessary information to be able to perform 
successful observations with the \gls{GBT}.
\begin{itemize}

\item In Chapter~\ref{chap:process} we briefly outline the features of the
\gls{GBT} and the general observing process.

\item in Chapter~\ref{chap:dss} you are introduced to the Dynamic Scheduling
System.

\item In Chapters~\ref{chap:astrid} and ~\ref{chap:datadisplay} we provide an
introduction to the \glsunset{Astrid}\gls{Astrid} observing interface and other
observing applications.

\item In Chapter~\ref{chap:scripts} we provide example \glspl{SB} that can 
be used in \gls{Astrid}.  We also provide detailed descriptions of the contents
of \glspl{SB}.

\item In Chapter~\ref{chap:tactics} we provide information on the strategies
that should be used and advanced techniques for observing with the \gls{GBT}.

\item Later chapters give basics of observing with various specific instruments:
Chapter~\ref{chap:vegas} for spectral line observing with \glsunset{VEGAS}\gls{VEGAS},
Chapter~\ref{chap:GUPPI} for pulsar observing with \glsunset{GUPPI}\gls{GUPPI},
Chapter~\ref{chap:kfpa} for observing with the \glsunset{KFPA}\gls{KFPA},
Chapter~\ref{chap:wband} for observing with the 4mm (68-92~GHz) receiver,
Chapter~\ref{chap:ccb} for continuum observing with the \glsunset{CCB}\gls{CCB},
%Chapter~\ref{chap:mustang} for mapping with the \glsunset{MUSTANG}\gls{MUSTANG} bolometer array,
Chapter~\ref{chap:vlba} for \glsunset{VLBI}\gls{VLBI} observing with the \gls{GBT}, and
Chapter~\ref{chap:radar} for solar system radar with the \gls{GBT}.

\item In Chapter~\ref{chap:rfi} we provide the locations of where to find more 
information about \glsunset{RFI}\gls{RFI}.

\item In Chapter~\ref{chap:weather} is a discussion of the effect of weather
conditions on observing.

\item In Chapters~\ref{chap:computing} and~\ref{chap:remote} we provide
information on computing and remote observing.

\item In Chapter~\ref{chap:travel} we provide information on what happens before
your observations and directions on getting to Green Bank.

\item In Chapter~\ref{chap:after} we provide information on how to take your data 
home with you and where to obtain the \gls{GBT} spectral line data reduction package,
\gls{GBTIDL}.


\item Additional information and special topics are covered in the Appendices.

\end{itemize}

New users should read Chapters~\ref{chap:process},~\ref{chap:dss},
~\ref{chap:astrid},~\ref{chap:datadisplay},~\ref{chap:scripts},~\ref{chap:tactics},
and~\ref{chap:computing} in their entirety.  They should also read the
remaining Chapters as needed.
