\chapter{Remote Observing With The GBT}\label{chap:remote}

%++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\section[Remote Observing Guidelines for Approved Projects]
{Remote Observing Guidelines for\\Approved Projects}

Permission to observe remotely must be explicitly granted by the Head of Science
Operations (currently Toney Minter) at least two weeks prior to the observing run.
Permission will be granted based on the appropriateness of the project and the
demonstrated experience of the observer.  If you wish to become authorized for remote
observations, please contact your assigned \gls{GBT} \dq{Friend}. Guidelines for
approved remote observing projects are as follows.

\begin{itemize}[leftmargin=*]

\item Consult with your assigned \gls{GBT} \dq{Friend} at least two weeks prior to
observing time.
\item Ensure your contact details in the \gls{DSS} (\htmladdnormallink
{https://dss.gb.nrao.edu}{https://dss.gb.nrao.edu/}) are current.
\item Prepare all \gls{Astrid} \glspl{SB} in advance.
\item Contact the telescope operator 30 minutes before the start of your observing
session.  You may use the \gls{CLEO} {\tt Talk and Draw} application (see
\S~\ref{sec:talkanddraw}) or call via telephone.  The contact number is
304--456--2346 or the Operator's direct line at 304--456--2341. x2346 connects to a
speaker phone and is the preferred number to use.  In case of a power outage, the direct
line to the control room is 304--456--3203. Provide the operator with all the
appropriate contact information.
\item Launch \gls{VNC} network displays of observing applications. Suggested \gls{VNC}
setup procedures are provided below.
\item Start up your observing applications immediately after contacting the operator.
These usually include
\begin{itemize}
\item {\bf CLEO} Open at least the {\tt Talk and Draw} windows, then any other \gls{CLEO}
application you need (see \S~\ref{sec:cleo}).
\item {\bf Astrid} The \gls{GBT} observing interface (see Chapter~\ref{chap:astrid}).
\item {\bf GBTIDL} The \gls{GBT} data reduction package (see \htmladdnormallink
{http://http://gbtidl.nrao.edu/}{http://http://gbtidl.nrao.edu/}).
\end{itemize}
\item When your observing time starts and the operator gives you security access
(puts you in the \dq{gateway}), you should put \gls{Astrid} into \dq{online} mode,
load your configuration and start observing.
\item At the end of your observations, put \gls{Astrid} into \dq{offline} mode and
remember to properly close your \gls{VNC} session using the \sq{\tt vncserver -kill}
command.
\end{itemize}


Please consult \htmladdnormallink
{https://safe.nrao.edu/wiki/bin/view/GB/Observing/GbtObservingPolicies}
{https://safe.nrao.edu/wiki/bin/view/GB/Observing/GbtObservingPolicies} and \\
\htmladdnormallink
{https://science.nrao.edu/facilities/gbt/observing/remote-observing-with-the-gbt}
{https://science.nrao.edu/facilities/gbt/observing/remote-observing-with-the-gbt}
for information on observing policies, remote observing and \gls{VNC} setup
instructions.
